---
title: "Data Analysis"
author: "Gilbert"
date: "12/3/2020"
output: png_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(stargazer)
library(ggpubr)
```
First, read data
```{r}
df_final <- read_csv("../Data/df_final.csv")
df_threat <- read_csv("../Data/df_threat.csv")
head(df_final)
head(df_threat)
```
Let's See how "China Threat" discourse varies over time.
```{r}
#plot China's Threat over time
china_threat_discourse_over_time <- 
  ggplot(df_threat, aes(x=year, y=threat_number, color=threat_type))+
  geom_line()+ #line plot
  scale_color_manual(values = c("blue", "green", "red", "black"), #line color
                     #legend labels
                     labels = c("Economic Threat", "Military Threat", 
                                "Political Threat", "Threat as a Whole"))+
  theme_classic()+ #classic theme
  labs(title="\"China Threat\" Discourse Over Time", #title
       y="Number of Articles Mentinoed \"China Threat\"", #x axis
       x="Year", #y axis
       color="Threat Type")+ #legends' title
  scale_x_continuous(n.breaks = 27)+ #add more ticks to x axis
  theme(axis.text.x = element_text(angle = 45, size=7)) #adjust x axis text
#display the plot
china_threat_discourse_over_time

#export the plot
ggsave(filename = "../Results/China_Threat_Discourse_Over_Time.png", 
       plot = china_threat_discourse_over_time)
```

Then, we plot a graph to show how "China Threat" discourse, its military and economic capabilities, and authoritarianism change over time.
```{r}
#plot China's Threat discourse over time
threat_over_time <- ggplot(df_final, aes(x=year, y=threat_total, group = 1))+
  geom_line()+ #line plot
  theme_classic()+ #classic theme
  labs(title = " \"China Threat\" Over Time", #plot title
      y = "Number of Articles", #y axis title
      x = "Year")+ #x axis title
  scale_x_continuous(n.breaks = 10)+ #specify number of ticks
  theme(axis.text.x = element_text(angle = 45, size=6), #x axis text
        axis.title.y = element_text(size=8), #y axis title size
        plot.title=element_text(size=9), #title size
        axis.title.x = element_text(size=8), #x axis title size
        axis.text.y = element_text(size=8))+ #y axis text
  scale_x_continuous(n.breaks = 10)
#plot China's military power over time
military_over_time <- ggplot(df_final, aes(x=year, y=military, group=1))+
  geom_line()+
  theme_classic()+
  labs(title="China's Changing Military Power Over Time",
       y="China's Military Expenditure",
       x = "Year")+
  theme(axis.text.x = element_text(angle = 45, size=6),
        axis.title.y = element_text(size=8), 
        plot.title=element_text(size=9), 
        axis.title.x = element_text(size=8),
        axis.text.y = element_text(size=8))+ 
  scale_x_continuous(n.breaks = 10)
#plot China's economic power over time
economy_over_time <- ggplot(df_final, aes(x=year, y=GDP, group=1))+
  geom_line()+
  theme_classic()+
  labs(title="China's Changing Economic Power Over Time",
       y="China's GDP",
       x = "Year")+
  theme(axis.text.x = element_text(angle = 45, size=6),
        axis.title.y = element_text(size=8), 
        plot.title=element_text(size=9), 
        axis.title.x = element_text(size=8),
        axis.text.y = element_text(size=8))+ 
  scale_x_continuous(n.breaks = 10)
#plot China's authoritarian level over time
polity_over_time <- ggplot(df_final, aes(x=year, y=polity, group=1))+
  geom_line()+
  theme_classic()+
  labs(title="China's Authoritarianism Over Time",
       y="China's Polity V Index",
       x = "Year")+
  theme(axis.text.x = element_text(angle = 45, size=6),
        axis.title.y = element_text(size=8), 
        plot.title=element_text(size=9), 
        axis.title.x = element_text(size=8),
        axis.text.y = element_text(size=8))+ 
  scale_x_continuous(n.breaks = 10)
#merge them together
china_threat_with_changing_capabilities <- 
  ggarrange(threat_over_time, military_over_time, economy_over_time, polity_over_time,
          ncol=2, nrow=2)
#display the plot
china_threat_with_changing_capabilities
#export the plot
ggsave(filename = "../Results/China_Threat_With_Changing_Capabilities.png",
       plot = china_threat_with_changing_capabilities)
```
Let's see how "China Threat" discourse varies with China's changing military and economic capabilities and its authoritarian level.
```{r}
#plot the relationship between China's economy power and China threat discourse
economy_threat <- ggplot(df_final, aes(x=GDP, y=economy_threat))+
  geom_point()+ #point plot
  geom_smooth(color="red")+ #do a regression
  theme_classic()+ #use classic theme
  labs(title="China's Economic Power and China as Economic Threat", #add title
       y="China Economic Threat", #change y axis title
       x="China's GDP, logged")+ #change x axis title
  theme(axis.title.y = element_text(size=7), #y axis size
        plot.title=element_text(size=10), #title size
        axis.title.x = element_text(size=10))+ #x axis size
  scale_x_log10() #take log of the x axis
#plot the relationship between China's military power and China threat discourse
military_threat <- ggplot(df_final, aes(x=military, y=military_threat))+
  geom_point()+
  geom_smooth(color="red")+
  theme_classic()+
  labs(title="China's Military Power and China as Military Threat",
       y="China Military Threat",
       x="China's Military Expenditure, logged")+
  theme(axis.title.y = element_text(size=7),
        plot.title=element_text(size=10), 
        axis.title.x = element_text(size=10))+
  scale_x_log10()
#plot the relationship between China's polity level and China threat discourse
polity_threat <- ggplot(df_final, aes(x=polity, y=political_threat))+
  geom_point()+
  geom_smooth(color="red")+ #this won't display because there is no correlation
  theme_classic()+
  labs(title="China's Political Regime and China as Political Threat",
       y="China Political Threat",
       x="China's Authoritarianism Level")+
  theme(axis.title.y = element_text(size=7),
        plot.title=element_text(size=10), 
        axis.title.x = element_text(size=10)) 
#merge them together
regression_plot <- ggarrange(economy_threat, military_threat, polity_threat,
          ncol=1, nrow=3)
#display the plot
regression_plot
#expot the plot
ggsave(filename = "../Results/Regression_Plot.png",
       plot = regression_plot)
```
Finally, do a linear regression!
```{r}
mod1 <- lm(formula = economy_threat ~ log(GDP), data=df_final)
mod2 <- lm(formula = military_threat ~ log(military), data=df_final)
mod3 <- lm(formula = political_threat ~ polity, data=df_final)
mod4 <- lm(formula = threat_total ~ log(GDP)+log(military)+polity, data=df_final)

stargazer(mod1, mod2, mod3, mod4, title = "Regression Results", 
          #output type
          type = "html",
          #omit constant row
          omit = "Constant",
          #write the regression table
          out = "../Results/regression_table.html",
          #rows' names
          covariate.labels = c("China's GDP, logged", 
                               "China's military expenditure, logged",
                               "China's Authoritarianism"),
          #columns' names
          dep.var.labels = c("Economic Threat", 
                             "Military Threat",
                             "Political Threat",
                             "Threat Discourse as a Whole"),
          # add note
          notes = c("Model 3 is blank because, as the above plot shows, regression fails, with Polity index being constant.", "Model 4 is misleading, because \"China Threat\" discourse is driven by other factors (China's international action, I assume). However, since we only include economy, military, and polity here, regression does its job forcefully. Thus, here come the results we see."),
          notes.align = "l" ) #left align notes
```
It seems "China Threat" is not about who China is, but what China does. Let's identify what China did around the three highest peaks.
```{r}
  #let's mark the three highest peaks
plot_annotated <- china_threat_discourse_over_time+
  #add a rectangle
  annotate("rect", xmin=1996, xmax=1998, ymin=57, ymax=62, alpha=.2, fill=NA, color="red")+ 
  #add text
  annotate("text", x=2000, y=63, label="Lee Teng-hui President and China's missile test", size=3)+
  annotate("rect", xmin=2004, xmax=2006, ymin=45, ymax=50, alpha=.2, fill=NA, color="red")+
  annotate("text", x=2005, y=51, label="Anti-Secession Law toward Taiwan", size=3)+
  annotate("rect", xmin=2013, xmax=2015, ymin=40, ymax=45, alpha=.2, fill=NA, color="red")+
  annotate("text", x=2014, y=46, label="Taiwan's Sunfolower Movement", size=3)
#display the plot
plot_annotated
#export the plot
ggsave(filename = "../Results/Plot_Annotated.png",
       plot = plot_annotated)
```

