---
title: "Data Manipulation"
author: "Gilbert"
date: "12/2/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr) 
library(purrr) 
library(lubridate)
library(readxl)
```

First, we read orginal data, and remove repeated items and filter out items before 1991.12.26 when Soviet Union collapsed, because "China Threat" discourse emerged mainly since 1990s.
```{r}
#read the data we scraped from People's Daily website
df <- read_csv("../Data/webscraping_df.csv")
# clean it a little bit
df_tidied <- df %>% 
  #filter out items before 1991.12.26
  filter(date > ymd("1991-12-26")) %>% 
  #filter out repeated items
  filter(!duplicated(titles))
#create a China_threat dataframe
China_threat <- df_tidied %>% 
  #extract year from date
  mutate(year = str_sub(date, 1, 4)) %>% 
  #count the number of China Threat articles within each year
  group_by(year) %>% 
  count(name = "threat_total")
```
Get China's Polity V data to measure China's authoritarianism. Since from People's Daily, we know that "China Threat" discurse appeared after 1992, and Polity V data only covers until 2018, we only select years between 1992 and 2018.
```{r}
#read data from Polity V
polity <- read_excel("../Data/p5v2018.xls")
#create a China_polity dataframe
China_polity <- polity %>% 
  #select columns we need
  select(country, polity, year) %>% 
  filter(country == "China", #filter out countries beside China
         year >= 1992 & year <= 2018) %>% #filter out years before 1992
  #since we only know that this data is China's
  select(!country) %>% 
  #since the first China_threat dataframe's year column is character
  mutate(year = as.character(year)) 
```
Get China's military expenditure and GDP data to measure China's military and economic capacity.
```{r}
#read military_expenditure data
military <- read_excel("../Data/military_raw.xls")
#read GDP data
economy <- read_excel("../Data/GDP_raw.xls")
#create a China_military dataframe
China_military <- military %>% 
  #filter out countries other than China
  filter(`Country Name` == "China") %>% 
  #remove uesless columns
  select(!c(`Country Code`, `Indicator Name`, `Indicator Code`, `2020`)) %>% 
  #filter out data before 1992 and after 2018
  select(1, 34:60) %>% 
  #tidy from wide to long
  gather(key = "year", value = "military", 2:28) %>% 
  #remove country name column becasue we know which country it is
  select(!"Country Name")

#do the same thing to economy data
China_economy <- economy %>% 
  filter(`Country Name` == "China") %>% 
  select(!c(`Country Code`, `Indicator Name`, `Indicator Code`, `2020`)) %>% 
  select(1, 34:60) %>% 
  gather(key = "year", value = "GDP", 2:28) %>% 
  select(!"Country Name")
```
Finally, categarize "China Threat" further into three types: China as a military threat, as an economic threat, and as a political threat. 
```{r}
categarized_threat <- df_tidied %>% 
  #once one type of threat is identified, I give its dummy variable: 1
  mutate(military=if_else(str_detect(text, "军"), 1, 0)) %>% #military threat
  mutate(economy=if_else(str_detect(text, "经济")|str_detect(text, "发展"),
                         1, 0)) %>% #economic threat
  mutate(polity=if_else(str_detect(text, "政治")|str_detect(text, "社会主义")|
                         str_detect(text, "意识形态")|str_detect(text, "制度"),
                        1, 0)) %>% #political threat
  mutate(year = str_sub(date, 1, 4)) %>% #transform date to year
  #sum different types of threat
  group_by(year) %>% 
  summarize(military_threat = sum(military),
            economy_threat = sum(economy),
            political_threat = sum(polity))
```

Merge data
```{r}
#merge four dataframes together
df_final <- China_threat %>% 
  left_join(China_economy, by = "year") %>% 
  left_join(China_military, by = "year") %>% 
  left_join(China_polity, by = "year") %>% 
  left_join(categarized_threat, by = "year") %>% 
  #remove 2019, 2020 data, which contain NAs
  filter(!is.na(GDP))
```
Write a csv file
```{r}
write_csv(df_final, "../Data/df_final.csv")
```
To do the job of plotting different types of threat, I also need a long dataframe exclusively for this purpose.
```{r}
#tidy the dataframe to the long format
df_threat <- df_final %>% 
  #select variables we need
  select(year, threat_total, military_threat, economy_threat, political_threat) %>% 
  #tidyr!
  gather(key = "threat_type", value = "threat_number", 2:5)
#write a csv
write_csv(df_threat, "../Data/df_threat.csv")
```

